Secontrails plots

### 2022-01-17 R/Secontrails plots.Rmd
Work on scd trails
run all version

# Outputs
```{r}
secondtrails$TrailsDensity

secondtrails$paths # 'paths'
class(secondtrails$paths) # SpatialLines (sp)

secondtrails$lines # 'lines' Sert à quoi ??
class(secondtrails$lines) # matrix

plot(secondtrails$SmoothedSecondTrails) # SmoothedSecondTrails
class(secondtrails$SmoothedSecondTrails) # sfc_MULTIPOLYGON

@@

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails$paths), col = "red")

@@

# With tree selection
```{r}
NewInventory <- treeselectionoutputs$inventory # scenario = "RIL3", objectivelax = TRUE

@@

# HarvestableUp <- sf::st_as_sf(
#   dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
#   coords = c("Xutm", "Yutm")) %>% 
#   st_set_crs(st_crs(HarvestablePolygons))

@@

# Future <- sf::st_as_sf(
#   dplyr::filter(NewInventory, LoggingStatus == "future"),
#   coords = c("Xutm", "Yutm")) %>% 
#   st_set_crs(st_crs(HarvestablePolygons))

@@

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails$paths), col = "red") +

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  # geom_sf(data = Future,
  #         aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  geom_sf(data = ProbedHollow,
          aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

@@

```{r}
ggplot() +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "P6 zones exploitables") +

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails[[3]]), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails[[1]]), col = "red") +

@@

  scale_colour_manual(values = c("Non-harvestable" = "grey",
                                 "Visible defect" = "pink", "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red", "Future" = "orange",
                                 "Reserve" = "purple", "Probed hollow" = "forestgreen")) +
  labs(color = "Logging status") +
  labs(title = "P6 EFI3 Hollow Fuel")
```

>>>>

# Outputs
```{r}
secondtrails$RawSecondTrails # 'non-smoothed secondary trails
class(secondtrails$RawSecondTrails) # SpatialLines (sp)
plot(st_as_sf(secondtrails$RawSecondTrails))

secondtrails$TrailsIdentity # information on sections of the trails
class(secondtrails$TrailsIdentity) # matrix

plot(secondtrails$SmoothedSecondTrails) # Smoothed Secondary Trails
class(secondtrails$SmoothedSecondTrails) # sfc_MULTIPOLYGON

@@

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails$RawSecondTrails), col = "red")

@@

# With tree selection
```{r}
NewInventory <- treeselectionoutputs$inventory # objectivelax = TRUE

@@

HarvestableUp <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "harvestableUp"),
  coords = c("Xutm", "Yutm")) %>%
  st_set_crs(st_crs(HarvestablePolygons))

@@

Future <- sf::st_as_sf(
  dplyr::filter(NewInventory, LoggingStatus == "future"),
  coords = c("Xutm", "Yutm")) %>%
  st_set_crs(st_crs(HarvestablePolygons))

@@

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails$RawSecondTrails), col = "red") +

  # Tree selection
  # geom_sf(data = NonHarvestable,
  #         aes(colour = "Non-harvestable"), show.legend = "point") +
  geom_sf(data = VisibleDefect,
          aes(colour = "Visible defect"), show.legend = "point") +
  # geom_sf(data = Future,
  #         aes(colour = "Future"), show.legend = "point", size = 4) +
  geom_sf(data = Reserve,
          aes(colour = "Reserve"), show.legend = "point", size = 4) +
  geom_sf(data = Harvestable,
          aes(colour = "Harvestable"), show.legend = "point", size = 4) +
  # geom_sf(data = HarvestableUp,
  #         aes(colour = "HarvestableUp"), show.legend = "point", size = 4) +
  geom_sf(data = Selected,
          aes(colour = "Selected"), show.legend = "point") +
  # geom_sf(data = ProbedHollow,
  #         aes(colour = "Probed hollow"), show.legend = "point") +
  geom_sf(data = MainTrails) +

@@

```{r}
# enregistré avec une hauteur = 1000 or 1100 or 1500

ggplot() +
  # Harvestable zones
  geom_sf(data = HarvestablePolygons,
          aes(alpha = Harvestable),
          fill = "olivedrab") +
  labs(alpha = "Harvestable") +
  labs(title = "P6 zones exploitables") +

  # 2ndary trails
  geom_sf(data = st_as_sf(secondtrails$SmoothedSecondTrails), col = "darkgreen") +
  geom_sf(data = st_as_sf(secondtrails$RawSecondTrails), col = "red") +

@@

  scale_colour_manual(values = c("Non-harvestable" = "grey",
                                 "Visible defect" = "pink", "Harvestable" = "skyblue",
                                 "HarvestableUp" = "blue", "Selected" = "red", "Future" = "orange",
                                 "Reserve" = "purple", "Probed hollow" = "forestgreen")) +
  labs(color = "Logging status") +
  labs(title = "Paracou P6 EFI3")

write.csv2(NewInventory, "C:/Users/Vincyane/Documents/Maria-pictures/ParacouP6_EFI3.csv") #  D:/VSC Kourou/Dataexemple
